High-Dimensional Regularized Discriminant Analysis

### 2016-01-11 reports/paper-hdrda.Rnw
Updated results summary with PDY's changes.

Similar to \cite{Witten:2011kc}, we report the average test error rates obtained
over 100 random training-test partitions in Table \ref{tab:microarray-results}
along with standard deviations of the test error rates in parentheses. The
\emph{HDRDA} and Guo classifiers were superior in classification performance for
the majority of the simulations with the popular Guo classifier providing
superior classification performance for the Burczysnki data set. Both
\emph{HDRDA} methods yielded comparable results.

@@

The average error-rate estimates for the Pang, Tong, and Witten classifiers were
comparable across all data sets. Furthermore, the average error rates for the
Pang and Tong classifiers were approximately equal throughout our study,
suggesting that the mean and variance estimators used in lieu of the MLEs
provided little improvement to classification accuracies. The random-forest
classifier was competitive only on the Singh data set. This result challenges
the claim of \cite{FernandezDelgado:2014ul} that the random forest is
typically superior. More studies should be performed to validate this statement
in the small-sample, high-dimensional setting.

Finally, the average test error rates for the Witten classifier were the largest
across all data sets. Given that the standard deviations were relatively large,
we hesitate to generalize claims regarding the Witten classifier being the
uniformly worst performer. However, the variability in its classification
accuracy across multiple random partitions of each data set were large enough to
rethink applying it in practice.

>>>>

Similar to \cite{Witten:2011kc}, we report the average test error rates obtained
over 100 random training-test partitions in Table \ref{tab:microarray-results}
along with standard deviations of the test error rates in parentheses. The
\emph{HDRDA} and Guo classifiers were superior in classification performance for
the majority of the simulations. The \emph{HDRDA} classifiers had the best
classification accuracy on the Chowdary and Shipp data sets. Although the random
forest's accuracy slightly exceeded the \emph{HDRDA} classifiers on the Tian
data set, our proposed methods outperformed the other classifiers considered.
Additionally, the \emph{HDRDA} classifiers had comparable performance on five of
the six data sets.

@@

The average error-rate estimates for the Pang, Tong, and Witten classifiers were
comparable across all data sets. Furthermore, the average error rates for the
Pang and Tong classifiers were approximately equal for all data sets except for
the Chiaretti dataset. This result suggests that the mean and variance
estimators used in lieu of the MLEs provided little improvement to
classification accuracies. However, we investigated the Pang classifier's poor
performance on the Chiaretti data set and determined that its variance estimator
exhibited numerical instability. The classifier's denominator was approximately
zero for both classes and lead to the poor classification performance.

The random-forest classifier was competitive when applied to the Chowdary and
Singh data sets and yielded the smallest error rate of the considered
classifiers on the Tian data set. The fact that the \emph{HDRDA} and Guo
classifiers typically outperformed the random-forest classifier challenges the
claim of \cite{FernandezDelgado:2014ul} that the random forest is typically
superior. Further studies should be performed to validate this statement in the
small-sample, high-dimensional setting.

Finally, the Pang, Tong, and Witten classifiers consistently yielded the largest
error rates across all data sets. Given that the standard deviations were
relatively large, we hesitate to generalize claims regarding the ranking of
these three classifiers in terms of error rate. However, the classifiers' error
rates and their variability across multiple random partitions of each data set
were large enough to rethink applying them in practice.
